\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-26 document/XSGRB_sample.tex
GRB100816A

	\subsection{GRB100814A (z=1.439)}
    The spectra presented here has not been published previously. The
    observations consists of three visits, the first beginning only 0.9 hours
    after the \textit{Swift} trigger, the other two visits were 2.13 and 98.40
    hours after the trigger, respectively. A bright afterglow continuum is
    present in all visits, allowing identification of absorption features
    belonging to a wide range of ions at $z=1.439$. A complex velocity structure
    in the absorption features belonging to \mgii, shows several components,
    separated by as much as 5000km/s, pointing to a likely merger scenario in
    the host.

>>>>

	\subsection{GRB100814A (z=1.439)}
    The spectra presented here has not been published previously. The
    observations consists of three visits, the first beginning only 0.9 hours
    after the \textit{Swift} trigger, the other two visits were 2.13 and 98.40
    hours after the trigger, respectively. A bright afterglow continuum is
    present in all visits, allowing identification of absorption features
    belonging to a wide range of ions at $z=1.439$. A complex velocity structure
    in the absorption features belonging to \mgii, shows several components,
    separated by as much as 500km/s, pointing to a likely merger scenario in
    the host.

	\subsection{GRB100816A (z=0.805)}
	The data presented here also formed the basis of GCN \#
	11123\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/11123.gcn3}}. The spectrum
	has not otherwise been published previously. This short GRB was observed 28.4
	hours after the GRB trigger. 4 x 1200 s of exposure reveals two distinct sets
	of emission lines, spatially offset $\lesssim 1 \arcsec $, very close in
	redshift space, $z=0.8034$ and $z=0.8049$, indicating either an interacting
	host or some complex velocity structure of the host. Faint underlying continua
	are present under both sets of lines.
